---
title: "1 - Install YOLO11"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1 - Install YOLO11}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 1.1 - Package installation

[`trackRai`](https://swarm-lab.github.io/trackRai) is currently not available on 
CRAN. However, you can install it directly from 
[GitHub](https://github.com/swarm-lab/trackRai/) as follows: 

```{r pgk_install, eval = FALSE}
pak::pak("swarm-lab/trackRai")
```

---

# 1.2 - YOLO installation

## 1.2.1 - Before installing YOLO

It is recommended to run `trackRai` on a machine equipped with an 
[NVIDIA](https://www.nvidia.com/) graphics card and the
[CUDA toolkit](https://developer.nvidia.com/cuda-toolkit). If your computer is 
equipped with an NVIDIA graphics card, you can find instructions to install CUDA 
here:

- For Windows computers: https://docs.nvidia.com/cuda/cuda-installation-guide-microsoft-windows/
- For Linux computers: https://docs.nvidia.com/cuda/cuda-installation-guide-linux/

Note that if your computer is not equipped with an NVIDIA graphics card or if 
the CUDA toolkit is not installed on it, you can still use `trackRai` but the 
training of the YOLO model may take a very long time (several hours).

## 1.2.2 - Installing YOLO

Once `trackRai` is installed, you will need to install 
[YOLO](https://www.ultralytics.com/yolo) on your machine using the helper 
function `install_yolo()` provided with `trackRai`. 

```{r setup, eval = FALSE}
library(trackRai)
install_yolo()
```

The installer will prompt you with a series of questions. Answer "Yes" every 
time if you want YOLO and its dependencies to be installed on your machine. 
Answering "No" will stop the installation process and `trackRai` will not be 
usable. 

---